Galaxy Zoo: Morphological Classifications for 120,000 Galaxies in HST Legacy Imaging

### 2016-09-07 response.md

We have added a paragraph in Section 4 for clarification.

-----------------------------------
Minor Comment 3
-----------------------------------

***3) In parts of Section 4.1, there is a confusing mix of f_mu,z and f_features, which appear to represent the same thing. Some clean-up (or additional explanation as to why they are different quantities) would be useful here.***

The main difference between Equations 2 and 4 is that the former is applied to the FERENGI calibration images and used to fit the normalization and zeta parameters. The latter uses the parameters to apply corrections to individual galaxies from the true data, and is the form implemented throughout the text.

We have added text to explicitly mark the difference between the two equations in what is now Section 4.2.

### 2016-09-07 writeup/gz_hubble_data_draft_2.tex
Confusing nomenclature (MiC 3); closes #179.

For the ``correctable'' sample of galaxies, we observe a decline in the vote fraction
\ffeatures{} with increasing simulated redshift for each unique galaxy. 
We model this relationship with a simple exponential
function which bounds $f_{\mu, z>0.3}$  between $f_{\mu, z=0.3}$ and 0:

@@

\noindent where $\hat\zeta$ is the correction factor applied to each galaxy as
a function of surface brightness. The best-fit parameters to the linear fit
(from least-squares optimization) are $\zeta_0=0.50$, $\zeta_1=-0.03$. To make the
final debiased correction, we use Equation~\ref{eqn:fzeta}, rearranged for clarity:

>>>>

For the ``correctable'' sample of galaxies, we observe a decline in the vote fraction
\ffeatures{} with increasing simulated redshift for each unique galaxy. 
We model this relationship \changes{for artificially-redshifted images} with a simple exponential
function which bounds $f_{\mu, z>0.3}$  between $f_{\mu, z=0.3}$ and 0:

@@

\noindent where $\hat\zeta$ is the correction factor applied to each galaxy as
a function of surface brightness. The best-fit parameters to the linear fit
(from least-squares optimization) are $\zeta_0=0.50$, $\zeta_1=-0.03$. To make the
final debiased correction \changes{for the genuine \hst{} data, we apply Equation~\ref{eqn:fzeta}:}
